Improving legitimacy and efficiency \\ of decisions in democratic communities

### 2017-09-04 statistical-quorum.tex
Write it out.
Even more things.

\begin{itemize}
\item We developed a framework of computing statistical credibility of results
based on sample size, votes cast, and voting duration.
\item Based on this framework we developed a concept of \emph{statistical quorum}
as a threshold of votes required to deem results legitimate.
\item We implemented an online application \emph{PeerMind},
integrating credibility of results and statistical quorum, and designed
a workflow of its use in a decision making processes.
\item We deployed the application in a democratically run community of 140
members for 5 months.
\item \todo[inline]{We did this analysis and found these results. Legitimacy. Efficiency. Attention.}
\end{itemize}

>>>>

\begin{itemize}
\item We developed a framework of computing statistical credibility of results
based on sample size, votes cast, and voting duration.
\item Based on this framework we developed a concept of \emph{statistical quorum}
as a threshold of votes required to deem results legitimate.
\item We implemented an online application \emph{PeerMind},
integrating credibility of results and statistical quorum, and designed
a workflow of its use in a decision making processes.
\item We deployed the application in a democratically run community of 140
members for 5 months.
\item We show how use of statistical quorum increases legitimacy of decisions,
improves utilization of collective attention, increases overall participation,
and increases number of decisions made while not sacrificing their legitimacy.
\end{itemize}
